%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.40in,top=0.3in,right=0.75in,bottom=0.1in]{geometry} % Document margins
\usepackage{fontawesome5}
\usepackage{times}
\usepackage[hidelinks]{hyperref}
\usepackage[scaled]{helvet}
\renewcommand\familydefault{\sfdefault} 
\usepackage[T1]{fontenc}
\usepackage{hyperref}
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}}
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
% \begin{center}
% {\centerline {\em \textbf {Seeking for a fulltime internship from Sep 2019 - Apr 2010(8 months) } } }
% \end{center}
\name{S\lowercase{tefano} B\lowercase{elli}} % Your name 


\address{\href{https://github.com/illeb}{\faGithub*{ illeb}} | \href{https://www.linkedin.com/in/stefano-belli/}{\faLinkedinIn{ Stefano Belli}} | \href{https://stackoverflow.com/users/1306679/illeb}{\faStackOverflow{ illeb }}}
\address{\faMapMarker*[regular]{ Borghi (FC), Italy} | \href{mailto://stefano.belli.dev@gmail.com}{\faEnvelope[regular]{ stefano.belli.dev@gmail.com}} | \faMobile*{ (+39) 331 5862768}}

\begin{document}
%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------


\begin{rSection}{Skills}

  \begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
  Languages: \ & Javascript, Typescript, C\#, HTML-CSS, Java, Python, SQL \\
  Frameworks \& Libs : \ & Angular, ReactJs, AngularJS, NodeJs, ExpressJs, ASP.NET Core, \\
  Process: \ & Agile, Scrum\\
  Tools: \ & Redux, RxJS, JsPlumb, GRPC, Webpack, Rollup.js, LESS, SASS, Azure, \\ \ & Jenkins, Jira\\
  
  %Frameworks \& Tools:
  %& {\textbf{Frontend: }} Angular, ReactJs, angularJs\\
  %& {\textbf{Backend: }} NodeJs, ExpressJs, ASP.NET Core\\
  %& {\textbf{Tools: }} Redux, RxJS, GRPC, Webpack, Rollup\\
  %& {\textbf{Testing: }} Jest, Jasmine, Karma\\
  %& {\textbf{Others: }} Agile, Scrum, Git, Azure,vvv,eeee\\
  \end{tabular}
\end{rSection}


\begin{rSection}{Work Experience}

  {\bf Radicalbit s.r.l} \hfill {\bf Full Remote}
  \\{\textit{Frontend Engineer}} \hfill {\em May 2021 - present}
  \begin{itemize}
    \item Developed a Continuous Intelligence app built in a
    microfrontend architecture (single-spa) with \\ ReactJs+Redux (saga).
    \item Designed and implemented various reusable components (in ReactJs) for the
    company design system.
    \item Created sdk libraries for GRPC-based communication to the
    backend's microservices.
  \end{itemize}
  {\bf Dynaset s.r.l.} \hfill  {\bf San Marino}
  \\{\textit{Lead Software Engineer}} \hfill {\em  March 2015 - May 2021}
  \begin{itemize}
    \item Led the development of
    \href{https://evohrplite.app/}{evohrp.lite}, a PWA application written in Angular 11+ in a Material-flavoured UI.
    \item Migrated the company main web app from angularJs to Angular11.
    \item Created CI/CD pipelines in Azure DevOps for streamlining deployment and testing of company products.
  \end{itemize}
  {\textit{FullStack developer}}
  \begin{itemize}
    \item Developed frontend interfaces using angularJs and Webpack 3+ as bundler.
    \item Created backend APIs using .NET Web Api 2 and Microsoft SQL Server.
  \end{itemize}
  
\end{rSection}

\begin{rSection}{Education}

{\bf University of Bologna, Italy } \hfill {\em 2015 - 2019} 
\\{ \textit {Master's degree in Computer Science, 104/110 }} 

{\bf University of Bologna, Italy } \hfill {\em 2012 - 2015} 
\\ { \textit {Bachelor's degree in Computer science, 98/110 }} \hfill
%Minor in Linguistics \smallskip \\
%Member of Eta Kappa Nu \\
%Member of Upsilon Pi Epsilon \\


\end{rSection}


% \begin{rSection}{Carrier Objective}
%  To work for an organization which provides me the opportunity to improve my skills and knowledge to grow along with the organization objective.
% \end{rSection}
%--------------------------------------------------------------------------------
%    Projects And Seminars
%-----------------------------------------------------------------------------------------------
\begin{rSection}{Projects}

{\bf \href{https://imagej.net/plugins/ds4h-image-alignment}{DS4H Image Alignment}}
\\ An ImageJ plugin specialized in co-registration of microscopic bidimensional images for histological examination.\\
Currently in use at IRST istitute in Meldola (FC). Built in Java.

{\bf \href{https://github.com/illeb/id3king}{Id3King}}
\\ A web app that collects and rearranges trekking data for easy trips planning.\\
Built in Angular and NodeJs.

\end{rSection}


\begin{rSection}{Interests}

  In the spare time tries to make something works with Arduinos and Home assistant, with poor results. \\Passionate about mycology, trekking and the usual nerds stuff (d\&d, w40k and mechanical
 keyboards).
\end{rSection}
\end{document}